Multi-task Mutual Learning for Vehicle Re-Identification

### 2019-04-04 paper.tex
Minor changes.

%%%%%%%%% TITLE
\title{Multi-modal task transfer learning for Vehicle Re-Identification}

@@

Due to the fact that vehicles are rigid objects, unlike people, the orientation of the vehicle can alter very predictably the appearance of in a particular viewpoint. Hence

In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks, an

@@

In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data.

@@

As we have two training sets, each of which contain different groundtruth labels, we adopt an alternate training schedule to optimise our model. We first train on our larger training set, which contains

>>>>

%%%%%%%%% TITLE
\title{Multi-task Mutual Learning for Vehicle Re-Identification}

@@

Due to the fact that vehicles are rigid objects, unlike people, the orientation of the vehicle can alter very predictably the appearance of in a particular viewpoint. \emph{TODO motivation and related work}

In this paper we propose a new mutual learning based network architecture, that aims to simulataneously learn a number of tasks and then use consensus learning to build an improved representation for the purpose of vehicle re-identification.

@@

In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data. \emph{TODO expand}

@@

As we have two training sets, each of which contain different groundtruth labels, we adopt an alternate training schedule to optimise our model. \emph{TODO}
